---
title: 'Data 605 Homework #3'
author: "Jean Jimenez"
date: "2023-09-13"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment 3

## Problem Set 1

### #1

What is the rank of the matrix A?

[1 2 3 4]

[-1 0 1 3]

A=

[0 1 -2 1]

[5 4 -2 -3]

To solve this problem, I inserted matrix A into R and used the rankMatrix() function

```{r}
#what is the rank of matrix A?

library(Matrix)
A=matrix(c(1,2,3,4,-1,0,1,3),nrow=4,ncol=4)

rank_A=rankMatrix(A)
rank_A
```

#### Answer

**The rank of matrix A is 2**

### #2

The maximum rank of a mxn matrix is n because rank is defined by the dimensions of column and row space. It cannot be more than n. The minimum rank of a non-zero matrix is 1 because it will at least have 1 row.

### #3

What is the rank of matrix B?

[1 2 1]

B= [3 6 3 ]

[2 4 2]

To solve this problem, I inserted matrix B into R and again used the rankMatrix() function.

```{r}
B=matrix(c(1,2,1,3,6,3,2,4,2),ncol=3, nrow=3)
rank_B=rankMatrix(B)
rank_B
```

#### Answer

The rank of matrix B is 1.

## Problem Set 2

Compute the convectors and eigenvalues of the given matrix.

For this question, I did the computation manually. Below is my work:

![](hw3%20problem%20set%202%20(1).jpg)

![](hw3%20problem%20set%202%20(2).jpg)

![](hw3%20problem%20set%202%20(3).jpg)

I will check my work with R below:

```{r}

D=matrix(c(1,2,3,0,4,5,0,0,6), nrow=3, ncol=3)

eigen(D)
```

My eigenvalues and eigenvectors match.
